---
title: "quickcheck tests generation"
author: "Willem Ligtenberg"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{quickcheck tests generation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(comment = "#>", collapse = TRUE)
```

Quickcheck is a package that allows randomised testing of functions. It implements a form of model based testing. Where you define the form the function arguments can take and then a test which needs to be true for a correct result.

For a more detailed description I would like to refer the reader to the [quickcheck](https://github.com/RevolutionAnalytics/quickcheck) github page.

When writing roxygen comments it is already useful to denote the type of the argument.
This type can then be used for model based testing, if we also supply the test.

This extention of roxygen implements the `@quickcheck` decorator for the test. To specify the type of the argument, the first word after the parameter is used (see example below).

```{r, eval = FALSE}
#' Add one to a numeric value
#' @param x numeric 
#' @return numeric x+1
#' @author Willem Ligtenberg
#' @export
#' @name plus_1
#' @quickcheck plus_1(x) == x+1
plus_1 <- function(x){
  return(x+1)
}
```

This will generate a file in the tests directory that will be executed during a normal R CMD check.
